R Notebook

### 2023-04-27 02_paper/02_study/02_fitbit paper/analysis_270423.Rmd
update_analysis

---
title: "Analysis 19.04.2023"
author: "Peer Keßler"
date: "`r Sys.Date()`"
output: html_document
---

@@

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
    #  lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse)

@@

# Correlation

```{r, warning=FALSE}
cache_corr <- 
  main %>% 
  clean_names() %>% 
  group_by(id) %>% 
  dplyr::summarize(`Mean Heartrate` = mean_heart,
            `Age` = age,
            `Teaching Experience` = teaching_experience,
            `Disruption Factor` = mean(disruption_factor, na.rm = T),
            `Confidence Factor` = mean(confidence_factor, na.rm = T)
            ) %>% 
  ungroup() %>% 
  distinct() %>% 
  select(!"id")

res <- rcorr(as.matrix(cache_corr))

knitr::kable(res[1], caption = "Pearson r")
knitr::kable(res[3], caption = "p Value")
```

```{r warning=FALSE,message=FALSE,error=FALSE}
corrplot(res$r, type="upper", order="hclust", sig.level = 0.05)
```

# Slopes, Intercepts

```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ))

table_data <- 
  df_regression %>% 
#  mutate(time = time * 60) %>% 
  split(.$Phase) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[[1]],
               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[[2]],
               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(intercept, digits = 3),
            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
            `p-Value (Intercept)` = round(intercept_p, digits = 3),
            `Mean(Slope)` = round(slope, digits = 3),
            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
            `p-Value (Slope)` = round(slope_p, digits = 3)
            )

@@

table_data %>% 
  arrange(Phase) %>% 
knitr::kable(., caption = "Overview")
```

# t-Test (Teaching Phase vs. Interview Phase)

Results:

```{r}
cache1 <- 
  main %>% 
  dplyr::select("ID","time","heart_rate_std", "heart_rate", "time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ ranef(.)$ID %>% 
        as_tibble(., 
                  rownames = "ID"
                  ) %>% 
        clean_names()
      ) %>% 
  bind_rows(.,
            .id = "time_span")

cache2 <-  
  main %>% 
  dplyr::select("ID","time","heart_rate_std", "heart_rate","time_span") %>% 
  distinct() %>% 
  mutate(ID = as_factor(ID)) %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
             data = .)) %>% 
  map(~ summary(.) %>% 
        .$coefficients %>% 
        .[c(1,2)]) %>% 
  bind_rows(.,
            .id = "time_span") %>% 
  pivot_longer(
  cols = everything(),
  names_to = "time_span",
  values_to = "mean_value"
  )

df_test <- 
  tibble(mean_intercept = cache2$mean_value[1:6],
         mean_time = cache2$mean_value[7:12],
         time_span = cache2$time_span[1:6]) %>% 
  right_join(x = .,
             y = cache1,
             by = "time_span") %>% 
  transmute(time_span,
            intercept = mean_intercept + intercept,
            time = mean_time + time,
            id = id)

t.test(df_test$intercept[df_test$time_span == "teaching"],
       df_test$intercept[df_test$time_span == "interview"],
       paired = TRUE)

t.test(df_test$intercept[df_test$time_span == "teaching"],
       df_test$intercept[df_test$time_span == "end"],
       paired = TRUE)
```

Cohen D:

```{r}
CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
       y = df_test$intercept[df_test$time_span == "interview"],
       pooled = T
       )

CohenD(x = df_test$intercept[df_test$time_span == "teaching"],
       y = df_test$intercept[df_test$time_span == "end"],
       pooled = T
       )
```

# Graphs for all Phases

```{r}
mods <-   
  df_regression %>% 
  split(.$time_span) %>% 
  map(~ lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      )

@@

# Different endings

```{r fig.width = 10,results='hide',fig.keep='all'}
df_survival <- 
  main %>% 
  filter(time_span == "overall") %>% 
  select("time","ID") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarise(max_time = max(time)) %>% 
  ungroup()

df_survival_analysis <- 
  tibble(time = seq(max(df_survival$max_time),
              min(df_survival$max_time),
              by = -1),
         p = NA)

n <- length(df_survival$ID)

for (i in seq(min(df_survival$max_time),
              max(df_survival$max_time),
              by = 1)) {

  p <- 
    df_survival %>%
    filter(max_time >= i) %>%
    pull(max_time) %>%
    length(.)

  df_survival_analysis$p[df_survival_analysis$time == i] <- p/n

}

p_80 <- 
  df_survival_analysis %>% 
  filter(p > 0.8) %>% 
  pull(time) %>% 
  max(.)

p_90 <- 
  df_survival_analysis %>% 
  filter(p > 0.9) %>% 
  pull(time) %>% 
  max(.)

df_survival_analysis %>% 
  ggplot(mapping = aes(x = time,
                       y = p
                       )
         ) + 
  geom_line() +
  geom_hline(yintercept = 0.8,
             linetype = "dashed"
             ) +
  geom_hline(yintercept = 0.9,
             linetype = "dashed"
             ) +
  geom_vline(xintercept = p_80,
             linetype = "dashed"
             ) +
  geom_vline(xintercept = p_90,
             linetype = "dashed"
             ) +
  labs(x = "Time (in Seconds)",
       y = "Relative Frequency") +
  scale_x_continuous(breaks=c(4500, 5000, p_90, 5500, p_80, 6500, 7000)) +
  scale_y_continuous(breaks=c(0.25, 0.5, 0.75, 0.8, 0.9, 1)) +
  theme_apa()
```

```{r fig.width = 10,results='hide',fig.keep='all'}
loess_plot_data_90 <- 
  main %>% 
  filter(time_span == "overall" &
         time <= p_90) %>%
  dplyr::select("heart_rate", "ID", "time") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)) %>%
  ungroup() %>% 
  right_join(x = .,
             y = distinct(select(main,
                          "ID","time_span", "time", "heart_rate"
                        )),
             by = "ID") %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

loess_plot_data_80 <- 
  main %>% 
  filter(time_span == "overall" &
         time <= p_80) %>%
  dplyr::select("heart_rate", "ID", "time") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)
            ) %>%
  ungroup() %>%  
  right_join(x = .,
             y = distinct(select(main,
                          "ID","time_span", "time", "heart_rate"
                        )),
             by = "ID") %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

loess_plot_data_all <- 
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("heart_rate", "ID", "time") %>% 
  distinct() %>% 
  group_by(ID) %>% 
  summarize(mean_heart = mean(heart_rate),
            sd_heart = sd(heart_rate)
            ) %>%
  ungroup() %>%  
  right_join(x = .,
             y = distinct(select(main,
                          "ID","time_span", "time", "heart_rate"
                        )),
             by = "ID") %>%
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart)

ggplot(mapping = aes(x = time,
                            y = heart_rate_std
                            )) +
  geom_smooth(data = loess_plot_data_80,
              aes(color = "80%"),
              se = F
              ) +
  geom_smooth(data = loess_plot_data_90,
              aes(color = "90%"),
              se = F) +
  geom_smooth(data = loess_plot_data_all,
              aes(color = "Baseline"),
              linetype = "dashed",
              se = F) +
  labs(x = "Time (in Seconds)",
       y = "Average Heart Rate (Standardized)",
       color = "Legend") +
  scale_color_manual(values = c("80%" = "blue", "90%" = "red", "Baseline" = "black")) +
  theme_apa()
```

# Robustness

```{r fig.width = 10,results='hide',fig.keep='all'}
linear_plot_data_80 <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time", "heart_rate") %>% 
  distinct() %>% 
  left_join(x = .,
            y = distinct(select(.data = loess_plot_data_80,
                       "ID", "mean_heart", "sd_heart")),
            by = "ID"
            ) %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart,
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

linear_plot_data_90 <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time", "heart_rate") %>% 
  distinct() %>% 
  left_join(x = .,
            y = distinct(select(.data = loess_plot_data_90,
                       "ID", "mean_heart", "sd_heart")),
            by = "ID"
            ) %>% 
  mutate(heart_rate_std = (heart_rate - mean_heart)/
           sd_heart,
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

linear_plot_data_all <-
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  distinct() %>% 
  mutate(Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ))

ggplot(mapping = aes(x = time,
                     y = heart_rate_std
                     )
       ) +
  # geom_point(alpha = 0.05) +
  geom_smooth(data = linear_plot_data_80,
              method = "lm",
              se = FALSE,
              size = 0.5,
              mapping = aes(color = "80%")
              ) +
  geom_smooth(data = linear_plot_data_90,
              method = "lm",
              se = FALSE,
              size = 0.5,
              mapping = aes(color = "90%")
              ) +
  geom_smooth(data = linear_plot_data_all,
              method = "lm",
              se = FALSE,
              size = 0.5,
              linetype = "dashed",
              mapping = aes(color = "Baseline")
              ) +
  scale_color_manual(values = c("80%" = "blue", "90%" = "red", "Baseline" = "black")) + 
  labs(x = "Time (in Seconds)",
       y = "Average Heart Rate (Standardized)",
       color = "") +
  facet_grid(cols = vars(Phase)) +
  theme_apa()
```

@@

loess_plot_overall <-
  main %>% 
  filter(time_span == "overall") %>%
  dplyr::select("ID","time_span", "time","heart_rate_std") %>% 
  distinct() %>% 
  ggplot(mapping = aes(x = time,
                       y = heart_rate_std
                       )
         ) +
  # geom_point(alpha = 0.05) + 
  geom_smooth(se = FALSE,
              size = 0.5,
              colour = "black") +
  scale_color_viridis_d(option = "A",
                        end = 0.8) +
  scale_linetype_manual(values = c(1, 6)) +
  scale_x_continuous(expand = c(0, NA),
                     breaks = seq(0, 9000, 600)) +
  scale_y_continuous(breaks = seq(-1, 1, 0.5)) + 
  labs(x = "Time (in Seconds)",
       y = "") +
  ggtitle("Overall Course of Average Heartrate") +
  theme_apa() + 
  theme(axis.title.y = element_blank())
```

t-Test mit Mittelwerten -> teaching vs. interview & teaching vs. end & interview vs. end

>>>>

---
title: "R Notebook"
output: html_notebook
---

@@

```{r}
library(needs)
needs(ltm,
      xtable,
      broom,
      ppcor,
      jtools,
      lm.beta,
      janitor,
      lubridate,
      readxl,
      ggthemes,
      gridExtra,
      imputeTS,
      DescTools,
      cowplot,
      rstatix,
      ggpubr,
      lme4,
      lmerTest,
      viridis,
      gridExtra,
      gridtext,
      magrittr,
      PerformanceAnalytics,
      Hmisc,
      corrplot,
      tidyverse)

@@

# Slopes and Intercepts

```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std","heart_rate") %>% 
  distinct() %>% 
  mutate(time = time / 60) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

fix_models <-
  df_regression %>%
  split(.$Phase) %>%
  map( ~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
            data = .)) %>%
  map(
    ~ coef(.) %>%
      tibble::as_tibble(.,
                        rownames = "name") %>%
      transmute(
        type = if_else(str_detect(name,
                                  ":"),
                       true = "slope",
                       false = "intercept"),
        id = str_remove_all(name,
                            "[^[:digit:]]"),
        value = value
      ),

  ) %>%
  bind_rows(.id = "Phase") %>%
  pivot_wider(names_from = type,
              values_from = value)

p.values_slope <-
  fix_models %>%
  split(.$Phase) %>%
  map( ~ t.test(x = .$slope,
                mu = 0)$p.value) %>%
  bind_rows(.id = "Phase") %>%
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_slope")

p.values_intercept <-
  fix_models %>%
  split(.$Phase) %>%
  map( ~ t.test(x = .$intercept,
                mu = 0)$p.value) %>%
  bind_rows(.id = "Phase") %>%
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_intercept")

sd_mean <-
  fix_models %>%
  group_by(Phase) %>%
  summarize(
    mean_slope = mean(slope),
    sd_slope = sd(slope),
    mean_intercept = mean(intercept),
    sd_intercept = sd(intercept)
  )

table_data <- 
  right_join(x = sd_mean,
             y = p.values_intercept,
             by = "Phase") %>% 
  right_join(x = .,
             y = p.values_slope,
             by = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = mean_intercept,
            `SD(Intercept)` = sd_intercept,
            `p-Value (Intercept)` = p.value_intercept,
            `Mean(Slope)` = mean_slope, 
            `SD(Slope)` = sd_slope,
            `p-Value (Slope)` = p.value_slope, 
            ) %>% 
  arrange(Phase)

@@

table_data %>% 
  knitr::kable(.)
```

# Plots for all phases

```{r}
mods <-   
  df_regression %>% 
  split(.$time_span) %>% 
  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .
       )
      )

@@

# t-Tests

using heart rate means

```{r}
df_ttest <- 
  df_regression %>% 
  group_by(ID, time_span) %>% 
  summarize(mean_heart_rate = mean(heart_rate_std)) %>% 
  ungroup()
```

## Teaching vs. Interview

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "interview"],
         paired = T)

df_ttest %$% 
  CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "interview"],
         pooled = T)
```

## teaching vs. end

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "end"],
         paired = T)

df_ttest %$% 
  CohenD(x = .$mean_heart_rate[.$time_span == "teaching"],
         y = .$mean_heart_rate[.$time_span == "end"],
         pooled = T)
```

## interview vs. end

```{r}
df_ttest %$% 
  t.test(x = .$mean_heart_rate[.$time_span == "interview"],
         y = .$mean_heart_rate[.$time_span == "end"],
         paired = T)

df_ttest %$% 
  CohenD(x = .$mean_heart_rate[.$time_span == "interview"],
         y = .$mean_heart_rate[.$time_span == "end"],
         pooled = T)
```

# Multiple Linear Regression

# Pre Teaching Phase

@@

fit_pre_1 <-
   %>% 
  filter(time_span == "pre") %$% 
  lm(slope ~ mean_disruption)

fit_pre_2 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_confidence)

fit_pre_3 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_confidence + mean_disruption)

fit_pre_4 <-
  df_test_reg %>% 
  filter(time_span == "pre") %$% 
  lm(time ~ mean_confidence + mean_disruption + teaching_experience)

stargazer::stargazer(fit_pre_1, fit_pre_2,fit_pre_3, fit_pre_4,
                     type = "latex",
                     caption = "Pre Phase",
                     dep.var.labels = "Slope",
                     order = c(1, 3, 2),
                     covariate.labels = c("Disruption Factor",
                                          "Confidence Factor",
                                          "Teaching Experience"),
                     keep.stat = c("n","rsq","adj.rsq")
                     )
```
```
